AggregateCounts

### 2021-06-28 R/AggregateCounts.Rmd
Added code to remove bad samples, labels, compared across conditions and not species and color palette

```{r aggregate input}
aggregateList<-GetAggregates()#this reads the data from Matlab
# mutate(Strain = recode(Position, "0" = "Pa14 wt", "1"= "Pa14 -PA1414","2" = "Pa14 wt", "3"= "Pa14 -PA1414")) #this is to change the names
removable <- aggregateList %>% filter(Species == "Pa" & Condition == "mono")
aggregateList <- anti_join(aggregateList, removable)

#agregate input functions
#####
ReadAggregateFile<-function(file, species, timepoint, condition, replicate){#make a dataframe of the aggregate size list and add experimental parameters
  print(file)
   datos <-read.csv(file, header = F)  
   colnames(datos)<-c('Size') 
   datos<-datos %>% filter(!Size<0.5) #first filter the size
   datos<-datos %>% mutate(Species = species)#add parameters
   datos<-datos %>% mutate(TimePoint = timepoint) 
   datos<-datos %>% mutate(Condition = condition)
   datos<-datos %>% mutate(Replicate = replicate)
   datos$Species<-as.factor(datos$Species)
   datos$Replicate<-as.factor(datos$Replicate)
   datos$Condition<-as.factor(datos$Condition)
   datos$TimePoint<-as.factor(datos$TimePoint)
   return(datos)
}

GetAggregates<-function(){#import all experiments at once
   folder<- paste0('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Aggregate lists')
   fileList<-list.files(path = folder, full.names = TRUE)
   growthDf<-data.frame()
   for (aggList in 1:length(fileList)){
     fileName<-str_split(basename(fileList[aggList]), "\\.")[[1]][1]#this selects the base file name and removes the ".csv"
     attrList<-str_split(fileName,"_")[[1]]
     growthDf<-rbind(growthDf,ReadAggregateFile(fileList[aggList],attrList[4],attrList[2],attrList[1],attrList[3]))
     }
   return(growthDf)
}
#####
```
```{r aggregate wrangling and overview plots}
#Statistics from all aggregates

@@

#Plot agg summary per sample
#####
ggplot()+ 
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= meanAggSize, color = Species,shape = "MeanSize"),size = 3, height = 0, width = .1)+
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= maxSize, color = Species, shape = "MaxSize"),size = 3, height = 0, width = .1)+
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= biomass, color = Species, shape = "TotalBiomass"),size = 3, height = 0, width = .1)+  
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  facet_grid(. ~ Condition, scales = "free", space = "free") +
  ggtitle('Mean size and largest aggregate and total biomass per sample')+
  labs(x = "",y = bquote(paste("Volume (", mu*"m"^3*")")))+
  scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))
#####

#Get aggregate Summary per condition
aggregateListSummary<-aggregateList %>% group_by(Species, TimePoint, Condition) %>% 
  summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), seAggSize = std.error(Size), maxSize = max(Size), minSize = min(Size)) %>%
  ungroup() %>% mutate(RatioMaxTotal = maxSize/biomass ) 
#plot agg summary per condition
#####
ggplot()+
  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= meanAggSize, color = Species,shape = "MeanSize"),size = 3, height = 0, width = .1)+
  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= maxSize, color = Species, shape = "MaxSize"),size = 3, height = 0, width = .1)+
  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= biomass, color = Species, shape = "TotalBiomass"),size = 3, height = 0, width = .1)+ 
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  facet_grid(. ~ Condition, scales = "free", space = "free") +
  ggtitle('Mean size and largest aggregate and total biomass per sample')+
  labs(x = "",y = bquote(paste("Volume (", mu*"m"^3*")")))+
  scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))
#####
```
```{r non-fancy histogram}
#histogram<- hist(aggregateList$Size, breaks = c(0, 5, 10, 100, 1000, 10^9))#this is a simple way to do a histogram

@@

#Plot Normalized Frequency
#this isn't useful as the normalized Frequency changes with replicate, so it's better to pool all samples together
PlotHistSum<-function(rep.df,cond.df, y_var, title){
ggplot()+
    geom_jitter(data = HistReplicateSummary,aes(x=as.factor(LogBin),y=.data[[y_var]],  color =Species ),size=3, height = 0, width = .2, shape = 1)+
    geom_point(data = HistConditionSummary,aes(x=as.factor(LogBin),y=.data[[y_var]],  color =Species,group = Species),size=4, shape = 16, position = position_dodge(width = .3) )+
    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    facet_grid(Condition~TimePoint)+
    ggtitle(title)+
    labs(y = paste(y_var,"(%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}

@@

#Plot normalized Biomass per sample
##Pa
PlotHistRepBioTrend<-function(rep.df,species){
ggplot()+
    geom_line(data = rep.df %>% filter(Species==species),aes(x=as.factor(LogBin),y=NormalizedBiomass, color = Replicate, group = Replicate ),size=1)+
    guides(color = FALSE)+
    facet_grid(Condition~TimePoint)+
    labs(y = "Normalized Biomass",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    ggtitle(paste('Normalized Biomass per Sample', species))+
    theme_cowplot()+
    scale_colour_grey()+
    theme(plot.title = element_text(hjust = 0.5)) }
PlotHistRepBioTrend(HistReplicateSummary, "Pa")
PlotHistRepBioTrend(HistReplicateSummary, "Sa")

@@

##Summary df
aggsHistCondSum<-aggsHistCond %>% group_by(Species,Condition,TimePoint, Replicate, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint, Replicate) %>% mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))

@@

PlotHistSum(aggsHistRepSum,aggsHistCondSum,"NormalizedFrequency", "Normalized Frequency aggregates only")
PlotHistSum(aggsHistRepSum,aggsHistCondSum,"NormalizedBiomass","Normalized Biomass aggregates only")
PlotHistRepBioTrend(aggsHistRepSum, "Pa")
PlotHistRepBioTrend(aggsHistRepSum, "Sa")

@@

#Plot Frequency
ggplot()+
  geom_jitter(data = plankAggHistRep,aes(x=as.factor(Aggregation),y=AgPlNormFrequency,  color =Species, ),size=3, height = 0, width = .2, shape = 1)+ 
  geom_point(data = plankAggHistCond,aes(x=as.factor(Aggregation),y=AgPlNormFrequency,  color =Species,group = Species),size=4, shape = 16, position = position_dodge(width = .3) )+
  facet_grid(Condition~TimePoint)+
  ggtitle("Normalized Frequency (%) Aggs vs Plank")+
  labs(y = "Normalized Frequency (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
  theme_half_open()+
  panel_border() +
  #background_grid(major = "y")+
  theme(plot.title = element_text(hjust = 0.5)) 
#Plot Biomass
ggplot()+
    geom_jitter(data = plankAggHistRep,aes(x=as.factor(Aggregation),y=AgPlNormBiomass,  color =Condition ),size=2, height = 0, width = .2, shape = 1)+
  geom_jitter(data = plankAggHistCond,aes(x=as.factor(Aggregation),y=AgPlNormBiomass,  color =Condition,group = Species),size=5, shape = 16,height = 0, width = .2) +
    facet_grid(Species~TimePoint)+
  ggtitle("Normalized Biomass (%) Aggs vs Plank")+
    labs(y = "Normalized Biomass (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+  scale_color_manual( values = c( "red","blue","green", "gray"),labels = c("Sa Mono", "phz co", "pqsL co", "wt co"))+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5)) 
#####
```

@@

plankAggHistSummary<-plankAggHist %>% group_by(Species,TimePoint, Condition,Aggregation) %>%

@@

  geom_col(data = plankAggHistSummary,aes(x=Aggregation,y=MeanBiomass, fill = TimePoint),

@@

  geom_jitter(data = plankAggHist,aes(x=Aggregation,y=AgPlNormBiomass, group = TimePoint),shape = 1,size=2,position = position_dodge(width = .9),show.legend = FALSE)+
  geom_errorbar(data = plankAggHistSummary,aes(x=Aggregation,ymin=(MeanBiomass-SEBiomass), ymax = (MeanBiomass+SEBiomass), group = TimePoint),width = 0, size=.5,position = position_dodge(width = .9))+

@@

  facet_grid(.~Species)+
  scale_fill_grey()+

@@

          legend.position = c(0.79, 0.60))

@@

AggsOnlySummary<-aggsOnlyHistSummary.df %>% group_by(Species,TimePoint, Condition,LogBin) %>%

@@

    geom_col(data = AggsOnlySummary, aes(x=as.factor(LogBin),y=MeanFreq,  fill =TimePoint ),size=4,position = position_dodge( width = .9))+
    geom_jitter(data = aggsOnlyHistSummary.df, aes(x=as.factor(LogBin),y=NormalizedFrequency, group = TimePoint),shape = 1,size=2,position = position_dodge( width = .9))+
    geom_errorbar(data = AggsOnlySummary,aes(x=as.factor(LogBin),ymin=(MeanFreq-SEFreq), ymax = (MeanFreq+SEFreq), group = TimePoint),width = 0, size= .5,position = position_dodge( width = .9))+
    facet_grid(.~Species)+
    labs(fill = "",y = "Aggregates per bin (% of total)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+

@@

    scale_y_continuous(limits = c(0,70), expand = expand_scale(mult = c(0, 0)))+
    scale_fill_grey()+

@@

          legend.position = c(0.79, 0.60))
    geom_col(data = AggsOnlySummary, aes(x=as.factor(LogBin),y=MeanBiomass,  fill =TimePoint ),size=4,position = position_dodge( width = .9))+
    geom_errorbar(data = AggsOnlySummary,aes(x=as.factor(LogBin),ymin=(MeanBiomass-SEBiomass), ymax = (MeanBiomass+SEBiomass), group = TimePoint),width = 0, size= .5,position = position_dodge( width = .9))+
    facet_grid(.~Species)+
    labs(fill = "",y = "Aggregates per bin (% of total)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    scale_fill_grey()+
          legend.position = c(0.79, 0.60))

@@

```{r fancy histogram of aggregates !!!deprecated}
#Create histograms
##this takes a long time, so consider running them in parts
allDataGrouped<-aggregateList %>% group_by(Species, TimePoint, Condition)#first do the correct grouping
#allDataGrouped<-aggregateList %>% group_by(Species, TimePoint, Condition, Sample)# this is to include sample on the distribution or keep it out
allDataList<- group_split(allDataGrouped)#create list of dataframes
allDataHistograms.5<-map2(allDataList, 5,TotalFancyHistogram)#apply histogram function to all items in the list
allDataHistograms.5df<- bind_rows(allDataHistograms.5)#bring them together

@@

```{r Histogram functions}
FancyHistogram<-function(df, sec){#my own way of doing histograms which includes the sum and mean of values whitin each bin
  results<-data.frame()
  for( i in 1:(length(sec)-1)){ 
    blah<-df %>% filter(Size > sec[i] &Size<=sec[i+1])%>%summarise(frequency = n(), avg = mean(Size),suma = sum(Size)) %>% mutate(bin = i, min = sec[i],max = sec[i+1])
    if(blah$frequency>0){ 
      results<-rbind(results, blah)} 
  }
  return(results) 
}
TotalFancyHistogram<-function(df,binsize){
  totalbiomass<-sum(df$Size)#total biomass per sample
  totalfrequency<-length(df$Size)#total number of objects
  upperLim<-max(df$Size)+binsize-(max(df$Size)%%binsize)#largest bin size based in largest object
  breaksSequence<-seq(0,upperLim,binsize)#this makes breaks every "binsize" 
  histogram<-FancyHistogram(df,breaksSequence)#apply "fancy histogram" to get distributions
  histogram%>%mutate(BiomassBin=suma/totalbiomass)->histogram#add column with proportion of biomass per bin
  histogram%>%mutate(Density=frequency/totalfrequency)->histogram#add column with proportion of counts per bin
  histogram%>%mutate(Species=df$Species[1])->histogram#add column maintaining sample and so on...
  histogram%>%mutate(Condition=df$Condition[1])->histogram
  histogram%>%mutate(TimePoint=df$TimePoint[1])->histogram
  histogram%>%mutate(Sample=df$Sample[1])->histogram
  return(histogram)
}
```

>>>>

```{r aggregate input}
aggregateList<-GetAggregates()#this reads the data from Matlab
#remove bad samples and irrelevant conditions
##first remove irrelevant conditions
removable <- aggregateList %>% filter(Species == "Pa" & Condition == "mono")
aggregateList <- anti_join(aggregateList, removable)
##bad samples
aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "mono_d1_03_Pa" & !SampleCode == "mono_d1_03_Sa")
aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "phz_d4_14_Pa" & !SampleCode == "phz_d4_14_Sa")
aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "pqsL_d4_02_Pa" & !SampleCode == "pqsL_d4_02_Sa")
aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "pqsL_d4_04_Pa" & !SampleCode == "pqsL_d4_04_Sa")
aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "pqsL_d4_10_Pa" & !SampleCode == "pqsL_d4_10_Sa")
aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "wt_d4_07_Pa" & !SampleCode == "wt_d4_07_Sa")

#add proper labels for plots
aggregateList$Species <- factor(aggregateList$Species, levels = c("Pa", "Sa"),labels = c('P. aeruginosa','S. aureus'))
aggregateList$Condition <- factor(aggregateList$Condition, levels = c("mono", "wt", "pqsL", "phz"),labels = c('Sa mono','wt co', 'pqsL co', 'phz co'))
aggregateList$TimePoint <- factor(aggregateList$TimePoint, levels = c("d1", "d4"),labels = c('Day 1','Day 4'))
#agregate input functions
ReadAggregateFile<-function(file, species, timepoint, condition, replicate, sampleCode){#make a dataframe of the aggregate size list and add experimental parameters
  print(file)
   datos <-read.csv(file, header = F)  
   colnames(datos)<-c('Size') 
   datos<-datos %>% filter(!Size<0.5) #first filter the size
   datos<-datos %>% mutate(Species = species)#add parameters
   datos<-datos %>% mutate(TimePoint = timepoint) 
   datos<-datos %>% mutate(Condition = condition)
   datos<-datos %>% mutate(Replicate = replicate)
   datos<-datos %>% mutate(SampleCode = sampleCode)
   datos$Species<-as.factor(datos$Species)
   datos$Replicate<-as.factor(datos$Replicate)
   datos$Condition<-as.factor(datos$Condition)
   datos$TimePoint<-as.factor(datos$TimePoint)
   return(datos)
}
GetAggregates<-function(){#import all experiments at once
   folder<- paste0('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Aggregate lists')
   fileList<-list.files(path = folder, full.names = TRUE)
   growthDf<-data.frame()
   for (aggList in 1:length(fileList)){
     fileName<-str_split(basename(fileList[aggList]), "\\.")[[1]][1]#this selects the base file name and removes the ".csv"
     attrList<-str_split(fileName,"_")[[1]]
     growthDf<-rbind(growthDf,ReadAggregateFile(fileList[aggList],attrList[4],attrList[2],attrList[1],attrList[3], fileName))
     }
   return(growthDf)
}
```

```{r aggregate wrangling and overview plots}
#Statistics from all aggregates

@@

#Plot agg summary per sample
#####

ggplot()+ 
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= meanAggSize, color = Condition,shape = "MeanSize"),size = 3, height = 0, width = .3)+
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= maxSize, color = Condition, shape = "MaxSize"),size = 3, height = 0, width = .3)+
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= biomass, color = Condition, shape = "TotalBiomass"),size = 3, height = 0,width= .3)+
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  facet_grid(.~Species, scales = "free", space = "free") +
  ggtitle('Mean size and largest aggregate and total biomass per sample')+
  labs(x = "",y = bquote(paste("Volume (", mu*"m"^3*")")))+
  scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
  scale_color_brewer(palette = "Set1")+
  theme_cowplot()+
  panel_border() +
  theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background

#Get aggregate Summary per condition
aggregateListSummary<-aggregateList %>% group_by(Species, TimePoint, Condition) %>% 
  summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), seAggSize = std.error(Size), maxSize = max(Size), minSize = min(Size)) %>%
  ungroup() %>% mutate(RatioMaxTotal = maxSize/biomass ) 
#plot agg summary per condition
#####
ggplot()+ 
  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= meanAggSize, color = Condition,shape = "MeanSize"),size = 3, height = 0, width = .3)+
  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= maxSize, color = Condition, shape = "MaxSize"),size = 3, height = 0, width = .3)+
  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= biomass, color = Condition, shape = "TotalBiomass"),size = 3, height = 0,width= .3)+
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  facet_grid(. ~ Species, scales = "free", space = "free") +
  ggtitle('Mean size and largest aggregate and total biomass per condition')+
  labs(x = "",y = bquote(paste("Volume (", mu*"m"^3*")")))+
  scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
  scale_color_brewer(palette = "Set1")+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
          strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))
#####
```

```{r Aggregate size bins}
#histogram<- hist(aggregateList$Size, breaks = c(0, 5, 10, 100, 1000, 10^9))#this is a simple way to do a histogram

@@

#Plot Normalized Frequency
#this isn't useful as the normalized Frequency changes with replicate, so it's better to pool all samples together
PlotHistSum<-function(rep.df,cond.df, y_var, title){
ggplot()+
    geom_jitter(data = HistReplicateSummary,aes(x=as.factor(LogBin),y=.data[[y_var]],  color =Condition ),size=3, height = 0, width = .2, shape = 1)+
    geom_point(data = HistConditionSummary,aes(x=as.factor(LogBin),y=.data[[y_var]],  color =Condition,group = Condition),size=4, shape = 16, position = position_dodge(width = .5) )+
    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    facet_grid(Species~TimePoint)+
    ggtitle(title)+
    labs(y = paste(y_var,"(%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    scale_color_brewer(palette = "Set1")+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}

@@

#Plot normalized Biomass per sample
##Pa
PlotHistRepBioTrend<-function(rep.df,species){
ggplot()+
    geom_line(data = rep.df %>% filter(Species==species),aes(x=as.factor(LogBin),y=NormalizedBiomass, color = Replicate, group = Replicate ),size=1)+
    guides(color = FALSE)+
    facet_grid(Condition~TimePoint)+
    labs(y = "Normalized Biomass",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    ggtitle(paste('Normalized Biomass per Sample', species))+
    theme_cowplot()+
    scale_colour_grey()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5)) }
PlotHistRepBioTrend(HistReplicateSummary, "P. aeruginosa")
PlotHistRepBioTrend(HistReplicateSummary, "S. aureus")

@@

##Summary df
aggsHistCondSum<-aggsHistCond %>% group_by(Species,Condition,TimePoint, Replicate, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint, Replicate) %>% mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))%>%ungroup()

@@

PlotHistSum(aggsHistRepSum,aggsHistCondSum,"NormalizedFrequency", "Normalized Frequency aggregates only")
PlotHistSum(aggsHistRepSum,aggsHistCondSum,"NormalizedBiomass","Normalized Biomass aggregates only")
PlotHistRepBioTrend(aggsHistRepSum, "P. aeruginosa")
PlotHistRepBioTrend(aggsHistRepSum, "S. aureus")

@@

#Plot Frequency
ggplot()+
  geom_jitter(data = plankAggHistRep,aes(x=as.factor(Aggregation),y=AgPlNormFrequency,  color =Condition ),size=3, height = 0, width = .2, shape = 1)+ 
  geom_point(data = plankAggHistCond,aes(x=as.factor(Aggregation),y=AgPlNormFrequency,  color =Condition,group = Condition),size=4, shape = 16, position = position_dodge(width = .3) )+
  facet_grid(Species~TimePoint)+
  ggtitle("Normalized Frequency (%) Aggs vs Plank")+
  labs(y = "Normalized Frequency (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
  theme_half_open()+
  panel_border() +
  scale_color_brewer(palette = "Set1")+
  theme(plot.title = element_text(hjust = 0.5)) 
#Plot Biomass
ggplot()+
  geom_jitter(data = plankAggHistRep,aes(x=as.factor(Aggregation),y=AgPlNormBiomass,  color =Condition ),size=2, height = 0, width = .2, shape = 1)+
  geom_point(data = plankAggHistCond,aes(x=as.factor(Aggregation),y=AgPlNormBiomass,  color =Condition),size=5, shape = 16, position = position_dodge2(width = .5)) +
  facet_grid(Species~TimePoint)+
  ggtitle("Normalized Biomass (%) Aggs vs Plank")+
  labs(y = "Normalized Biomass (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+ 
  theme_cowplot()+
  panel_border() +
  scale_color_brewer(palette = "Set1")+
  theme(plot.title = element_text(hjust = 0.3)) 
#####
```

@@

plankAggHistSummary<-plankAggHistRep %>% group_by(Species,TimePoint, Condition,Aggregation) %>%

@@

  geom_col(data = plankAggHistSummary %>% filter(Aggregation=="Aggregate"),aes(x=Aggregation,y=MeanBiomass, fill = Condition),

@@

  geom_jitter(data = plankAggHistRep%>% filter(Aggregation=="Aggregate"),aes(x=Aggregation,y=AgPlNormBiomass, group = Condition),shape = 1,size=2,position = position_dodge(width = .9),show.legend = FALSE)+
  geom_errorbar(data = plankAggHistSummary%>% filter(Aggregation=="Aggregate"),aes(x=Aggregation,ymin=(MeanBiomass-SEBiomass), ymax = (MeanBiomass+SEBiomass), group = Condition),width = 0, size=.5,position = position_dodge(width = .9))+

@@

  facet_grid(TimePoint~Species)+
  scale_fill_brewer(palette = "Set1")+

@@

        legend.position = c(.45, 0.60))

@@

AggsOnlySummary<-aggsHistRepSum %>% group_by(Species,TimePoint, Condition,LogBin) %>%

@@

    geom_col(data = AggsOnlySummary, aes(x=as.factor(LogBin),y=MeanFreq,  fill =Condition ),size=4,position = position_dodge( width = .9))+
    geom_jitter(data = aggsHistRepSum, aes(x=as.factor(LogBin),y=NormalizedFrequency, group = Condition),shape = 1,size=2,position = position_dodge( width = .9))+
    geom_errorbar(data = AggsOnlySummary,aes(x=as.factor(LogBin),ymin=(MeanFreq-SEFreq), ymax = (MeanFreq+SEFreq), group = Condition),width = 0, size= .5,position = position_dodge( width = .9))+
    facet_grid(TimePoint~Species)+
    labs(fill = "",y = "Aggregates Frequency per bin (% of total)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+

@@

    #scale_y_continuous(limits = c(0,180), expand = expand_scale(mult = c(0, 0)))+
    scale_fill_brewer(palette = "Set1")+
          legend.position = c(0.79, 0.80))
AggsOnlySummaryRep<-aggsHistRepSum %>% group_by(Species,TimePoint, Replicate, Condition,LogBin) %>%
    geom_col(data = AggsOnlySummary, aes(x=as.factor(LogBin),y=MeanBiomass,  fill =Condition ),size=4,position = position_dodge( width = .9))+
    geom_errorbar(data = AggsOnlySummary,aes(x=as.factor(LogBin),ymin=(MeanBiomass-SEBiomass), ymax = (MeanBiomass+SEBiomass), group = Condition),width = 0, size= .5,position = position_dodge( width = .9))+
    facet_grid(TimePoint~Species)+
    labs(fill = "",y = "Biomass contribution per bin (% of total)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    scale_fill_brewer(palette = "Set1")+

@@

          legend.position = c(0.79, 0.80))

@@

```{r fancy histogram of aggregates !!!deprecated}
#Create histograms
##this takes a long time, so consider running them in parts
allDataGrouped<-aggregateList %>% group_by(Species, TimePoint, Condition)#first do the correct grouping
#allDataGrouped<-aggregateList %>% group_by(Species, TimePoint, Condition, Sample)# this is to include sample on the distribution or keep it out
allDataList<- group_split(allDataGrouped)#create list of dataframes
allDataHistograms.5<-map2(allDataList, 5,TotalFancyHistogram)#apply histogram function to all items in the list
allDataHistograms.5df<- bind_rows(allDataHistograms.5)#bring them together

@@

```{r Histogram functions}
FancyHistogram<-function(df, sec){#my own way of doing histograms which includes the sum and mean of values whitin each bin
  results<-data.frame()
  for( i in 1:(length(sec)-1)){ 
    blah<-df %>% filter(Size > sec[i] &Size<=sec[i+1])%>%summarise(frequency = n(), avg = mean(Size),suma = sum(Size)) %>% mutate(bin = i, min = sec[i],max = sec[i+1])
    if(blah$frequency>0){ 
      results<-rbind(results, blah)} 
  }
  return(results) 
}
TotalFancyHistogram<-function(df,binsize){
  totalbiomass<-sum(df$Size)#total biomass per sample
  totalfrequency<-length(df$Size)#total number of objects
  upperLim<-max(df$Size)+binsize-(max(df$Size)%%binsize)#largest bin size based in largest object
  breaksSequence<-seq(0,upperLim,binsize)#this makes breaks every "binsize" 
  histogram<-FancyHistogram(df,breaksSequence)#apply "fancy histogram" to get distributions
  histogram%>%mutate(BiomassBin=suma/totalbiomass)->histogram#add column with proportion of biomass per bin
  histogram%>%mutate(Density=frequency/totalfrequency)->histogram#add column with proportion of counts per bin
  histogram%>%mutate(Species=df$Species[1])->histogram#add column maintaining sample and so on...
  histogram%>%mutate(Condition=df$Condition[1])->histogram
  histogram%>%mutate(TimePoint=df$TimePoint[1])->histogram
  histogram%>%mutate(Sample=df$Sample[1])->histogram
  return(histogram)
}
```
```{r Test color palettes}
library(RColorBrewer)
brewer.pal(n = 4, name = 'Set1')
```
